\input{title.tex}

### 2023-05-06 docs/papers/01_manuscript/out/compiled_v-2.0.2.tex
refactor(project): :recycle: 重构到JH的风格

The validity of our theoretical analysis is supported by two facts:
(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
(2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares \cite{wang2019a, wang2019d}.

@@

The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

@@

% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
\begin{itemize}
    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
    \item \textbf{1998}: Implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
\end{itemize}

>>>>

The validity of our theoretical analysis is supported by two facts:
(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019e, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
(2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares \cite{wang2019e, wang2019d}.

@@

The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019e}.
Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

@@

% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019e}:
\begin{itemize}
    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019d, wang2019e}.
    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
    \item \textbf{1998}: Implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019d,wang2019e}.
    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
\end{itemize}

### 2023-05-06 docs/papers/01_manuscript/study_area.tex
refactor(project): :recycle: 重构到JH的风格

The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019, wang2019a}.
(2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
(3) In $1998$, the Unified Basinal Regulation was implemented (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
% 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019,wang2019a}.
(5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

>>>>

The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
(2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
(3) In $1998$, the Unified Basinal Regulation was implemented (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
% 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019d,wang2019e}.
(5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

### 2023-05-06 docs/papers/02_appendix/04_theoretical_model.tex
refactor(project): :recycle: 重构到JH的风格

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
	\caption{
		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}\label{fig:model}
\end{figure}

For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).

@@

\paragraph{Setup}

To understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic marginal benefits analysis to analyze how institutional mismatch could have led to the changes in water use, especially among provinces with high incentives for excess water use. Specifically, we modeled individual provincial decision-making in water resources before quota execution.

We proposed three intuitive and general assumptions:

@@

\begin{ass}
 (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant $C$.
\end{ass}
\begin{ass}
(Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
\end{ass}
Under the above assumptions, we can demonstrate three cases to simulate the water use decision-making and water use patterns in a whole basin.

@@

 %case1
\begin{case} Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.

@@

 %case2
 \begin{case} Mismatched institution: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.

 The water quota is determined at $t$=0 and imposed in $t$=1,2,... Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:

@@

 %case3
 \begin{case} Matched institution: This case corresponds to the institution under which water use in a basin is centrally managed.

@@

Proposition 1: Compared with the decentralized institution, a matched institution with unified management decreases total water use.

@@

Extensions of the model are shown in Supplementary Material S3.%%%

%Appendix的模型和proposition推导细节部分
%放在Appendix
Appendix: Water Use Optimization

%case1
\begin{case_appendix}Centralized decision

@@

\end{case_appendix}

%case2
 \begin{case_appendix}Decentralized decision

When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
Hence, the optimal water use in province i at period t, denoted as $\hat x_i^*$, satisfies $P \cdot A \cdot F'(x_{it})=\frac{C}{N}$, i.e., $A \cdot F'(x)=\frac{C}{P \cdot N}$.
Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.
\end{case_appendix}

%case3
 \begin{case_appendix}Forward-looking decentralized decision under quota restrictions

@@

The difference between $\widetilde x_i^*$ and $\hat x_i^*$ (i.e., $\frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$) represents the incentive of water overuse derived from an expectation of water quota allocation. The incentive of water overuse increases by A.
\end{case_appendix}

>>>>

For interpretation of the pattern of provincial water uses, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C).

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
	\caption{
		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see the proofs below.)}
\end{figure}

Below are the detailed theoretical model derivation process, where we started from proposing three intuitive and general assumptions:

@@

\begin{ass}
 (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant $C$.
\end{ass}
\begin{ass}
(Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
\end{ass}

@@

 %case1
\begin{case} before 1987: This case corresponds to a situation without any high-level water allocation institution.

@@

 %case2
 \begin{case} from 1987 to 1998: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.

 The water quota is determined at $t$=0 and imposed in $t$=1,2, \ldots Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:

@@

 %case3
\begin{case} after 1998: This case corresponds to the institution under which water use in a basin is centrally managed.

@@

Proposition 1: Compared with the decentralized institution, a institution with unified management decreases total water use.

@@

%Appendix的模型和proposition推导细节部分
%放在Appendix

%case1

@@

When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
Hence, the optimal water use in province i at period t, denoted as $\hat x_i^*$, satisfies $P \cdot A \cdot F'(x_{it})=\frac{C}{N}$, i.e., $A \cdot F'(x)=\frac{C}{P \cdot N}$.
Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.

@@

The difference between $\widetilde x_i^*$ and $\hat x_i^*$ (i.e., $\frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$) represents the incentive of water overuse derived from an expectation of water quota allocation. The incentive of water overuse increases by A.
